HyperLogLog: Exponentially Bad in Adversarial Settings

### 2022-01-26 docs/HLL_exp_bad/main.tex
adding harms section

>>>>

\subsection{Potential Harms and Mitigations}\label{sec-harms}

Our attacks are presented in a general way and evaluated either abstractly or in the context of a specific system described in the scientific literature~\cite{flexswitch}. We also propose an easily deployable countermeasure. Given this, we think the potential for harm to systems and individuals relying on HLL today is small. On the other hand, we hope our results will spur practitioners to consider the possibility of adversarial inputs in their specific applications and design accordingly. For the specific case of Redis, a real system that we analyse in detail, we have contacted the Redis core team and shared our results, following their advertised security policy.\footnote{\url{https://github.com/redis/redis/security/policy}.}
